### 2011-11-10 doc/pldi2012/code_ex.tex
fixed type of wires->nodes in code example

\lstset{
  captionpos=b,
  language=C++,
  basicstyle=\scriptsize,
  numbers=left,
  numberstyle=\tiny,
  columns=fullflexible,
  stepnumber=1,
  escapechar=\#,
  keepspaces=true,
  literate={<}{{$\langle$}}1 {>}{{$\rangle$}}1,
  morekeywords={region_relation,region,coloring,partition,spawn},
  deletekeywords=float,
}
\begin{lstlisting}[float={t},label={lst:code_ex},caption={Circuit Simulation Code Example}]
struct Node<rn>    { Node<rn>@rn next;    float charge, capacitance; }
struct Wire<rn,rn2,rw> { Wire<rn,rn2,rw>@rw next;
                                          Node<rn2>@rn in_node, out_node; float current, ... ; }
region_relation Circuit {
  region< Node<r_all_nodes> >                        r_all_nodes;
  region< Wire<r_all_nodes,r_all_nodes,r_all_wires> >       r_all_wires;
  Node<r_all_nodes>@r_all_nodes                   first_node;
  Wire<r_all_nodes,r_all_wires>@r_all_wires   first_wire;
}
region_relation CircuitPiece<rn, rw> {
  region< Node<rn_pvt+rn_shr> >                                 rn_pvt, rn_shr;
  region< Node<rn> >                                                   rn_ghost;
  region< Wire<rn_pvt+rn_shr+rn_ghost,rn,rw_pvt> >  rw_pvt;
  Node<rn_pvt+rn_shr>@(rn_pvt+rn_shr)                     first_node;
  Wire<rn_pvt+rn_shr+rn_ghost,rn,rw_pvt>@rw_pvt    first_wire;
  where rn_pvt $\le$ rn, rn_shr $\le$ rn, rn_ghost $\le$ rn, rw_pvt $\le$ rw;
};
void simulate_circuit(Circuit c) : RWE(c.r_all_nodes,c.r_all_wires)
{
  partition<c.r_all_wires> p_wires(wire_owner_map); // colored by piece they're in
  partition<c.r_all_nodes> p_nodes_pvs(node_sharing_map);
                                                                    // true = some neighbors in other pieces
  partition<p_nodes_pvs[false]> p_pvt_nodes(node_owner_map);
                                                                    // colored by piece they're in
  partition<p_nodes_pvs[true]> p_shr_nodes(node_owner_map);
                                                                    // colored by piece they're in
  partition<p_nodes_pvs[true]> p_ghost_nodes(node_nghbr_map);
                                                                    // colored by pieces they neighbor

>>>>

\lstset{
  captionpos=b,
  language=C++,
  basicstyle=\scriptsize,
  numbers=left,
  numberstyle=\tiny,
  columns=fullflexible,
  stepnumber=1,
  escapechar=\#,
  keepspaces=true,
  literate={<}{{$\langle$}}1 {>}{{$\rangle$}}1,
  morekeywords={region_relation,region,coloring,partition,spawn},
  deletekeywords=float,
}
\begin{lstlisting}[float={t},label={lst:code_ex},caption={Circuit Simulation Code Example}]
struct Node<rn>    { Node<rn>@rn next;    float charge, capacitance; }
struct Wire<rn,rn2,rw> { Wire<rn,rn2,rw>@rw next;
                                          Node<rn2>@rn in_node, out_node; float current, ... ; }
region_relation Circuit {
  region< Node<r_all_nodes> >                        r_all_nodes;
  region< Wire<r_all_nodes,r_all_nodes,r_all_wires> >       r_all_wires;
  Node<r_all_nodes>@r_all_nodes                   first_node;
  Wire<r_all_nodes,r_all_wires>@r_all_wires   first_wire;
}
region_relation CircuitPiece<rn, rw> {
  region< Node<rn_pvt+rn_shr> >                                 rn_pvt, rn_shr;
  region< Node<rn> >                                                   rn_ghost;
  region< Wire<rn_pvt+rn_ghost,rn,rw_pvt> >               rw_pvt;
  Node<rn_pvt+rn_shr>@(rn_pvt+rn_shr)                     first_node;
  Wire<rn_pvt+rn_ghost,rn,rw_pvt>@rw_pvt                first_wire;
  where rn_pvt #$\le$# rn, rn_shr #$\le$# rn, rn_ghost #$\le$# rn, rw_pvt #$\le$# rw;
};
void simulate_circuit(Circuit c) : RWE(c.r_all_nodes,c.r_all_wires)
{
  partition<c.r_all_wires> p_wires(wire_owner_map); // colored by piece they're in
  partition<c.r_all_nodes> p_nodes_pvs(node_sharing_map);
                                                                    // true = some neighbors in other pieces
  partition<p_nodes_pvs[false]> p_pvt_nodes(node_owner_map);
                                                                    // colored by piece they're in
  partition<p_nodes_pvs[true]> p_shr_nodes(node_owner_map);
                                                                    // colored by piece they're in
  partition<p_nodes_pvs[true]> p_ghost_nodes(node_nghbr_map);
                                                                    // colored by pieces they neighbor
